Type Refinements for the Working Class

### 2015-11-11 paper.tex
fix refs

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, let
  \[\Define{[\Omega]}{\coprod_{\MV{m}:v}
  \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}}\] Then for any
  $\Of{\mathcal{J}}{[\Omega]\to\Sets}$ we define the \emph{general judgment}
  $\GenJ{\Omega}{\mathcal{J}}$ as the section
  $\prod_{\omega\in[\Omega]}{\mathcal{J}(\omega)}$. Recall that metavariables
  have \emph{valences} rather than sorts; as such, the general judgment allows
  us to quantify over terms of higher type. However, for clarity we will often
  write $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.
\end{definition}

\begin{definition}[Hypothetical Judgment]
  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we have the
  hypothetical judgment
  $\Define{\HypJ{\mathcal{J}_2}{\mathcal{J}_1}}{\mathcal{J}_1\to\mathcal{J}_2}$.
  In other words, evidence for a hypothetical judgment is an effective
  transformation of evidence for the antecedent into evidence for the
  consequent. Note that this is the \emph{semantic} hypothetical judgment,
  which expresses admissibilities, rather than the \emph{syntactic}
  hypothetical judgment, which expresses derivabilities. We will not have any
  need for the latter.
\end{definition}

>>>>

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, let
  \[\Define{[\Omega]}{\coprod_{\MV{m}:v}
  \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}}\] Then for any family of judgments
  $\Of{\mathcal{J}}{[\Omega]\to\Sets}$ we define the \emph{general judgment}
  $\GenJ{\Omega}{\mathcal{J}}$ as the section
  $\prod_{\omega\in[\Omega]}{\mathcal{J}(\omega)}$. Recall that metavariables
  have \emph{valences} rather than sorts; as such, the general judgment allows
  us to quantify over terms of higher type. However, for clarity we will often
  write $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.
\end{definition}

\begin{definition}[Hypothetical Judgment]
  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we have the
  hypothetical judgment
  $\Define{\HypJ{\mathcal{J}_2}{\mathcal{J}_1}}{\mathcal{J}_1\to\mathcal{J}_2}$.
  In other words, evidence for a hypothetical judgment is an effective
  transformation of evidence for the antecedent into evidence for the
  consequent. Note that this is the \emph{semantic} hypothetical judgment,
  which expresses admissibilities, rather than the \emph{syntactic}
  hypothetical judgment, which expresses derivabilities \cite{harper:2016}. We
  will not have any need for the latter.
\end{definition}
